\documentclass[letterpaper, 11pt]{article}

% ATS
\input{glyphtounicode}
\pdfgentounicode=1

% Packages
\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage[parfill]{parskip}

% Fonts 
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{hyperref}
% Computer Modern Font %
\usepackage{lmodern}

% Margins 
\usepackage[top=0.4in, bottom=0.4in, left=0.4in, right=0.4in]{geometry}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\def\sectionlineskip{\medskip} 
\def\sectionskip{\medskip} 
\def\namesize{\LARGE}

% URLs (Discouraged)
\hypersetup{
    colorlinks=true,
    linkcolor=black,   
    urlcolor=black,
}

% Customizations
\usepackage{tabularx}
\usepackage{array}
\usepackage{titlesec}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\pagestyle{empty}
\urlstyle{same}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Resume Header
\newcommand{\ResumeHeader}[6]{
  \noindent
  \begin{tabularx}{\textwidth}{>{\centering\arraybackslash}X}
    \namesize\MakeUppercase{\textbf{\fullname}} \\
    #1 \textbar\ #2 \\
    #3 \textbar\ #4 \textbar\ #5 \textbar\ #6 \\
  \end{tabularx}
}

% Header Settings %
\def \fullname { Alan Matthew }

\def \linkedinlink { https://www.linkedin.com/in/alan-matthew-yk }
\def \linkedintext { linkedin.com/in/alan-matthew-yk }

\def \phonenumber { +65 8047 3599 }

\def \githublink { https://github.com/yokurang }
\def \githubtext { github.com/yokurang }

\def \emaillink { mailto:alan.matthew.yk@gmail.com }
\def \emailtext { alan.matthew.yk@gmail.com }

\def \websitelink { https://yokurang.github.io/ }
\def \websitetext { yokurang.github.io/ }

\def \address { 9 Jalan Membina, Singapore }

\def \headertype {\ResumeHeader}

\def \entryspacing {-0pt}

\def \linkedin {\href{\linkedinlink}{\linkedintext}}
\def \phone {{\phonenumber}}
\def \email {\href{\emaillink}{\emailtext}}
\def \github {\href{\githublink}{\githubtext}}
\def \website {\href{\websitelink}{\websitetext}}

\newcommand{\SectionHeading}[1]{
  \sectionskip
  \raggedright\raggedbottom\MakeUppercase{\large{#1}}
  \sectionlineskip
  \hrule
  \color{black}
}

% Entry with Title, Subheading, Date, Location % 
\newcommand{\ResumeEntryTSDL}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r} 
      \textbf{#1} & #2 \\
      #3 & #4 \\
    \end{tabular*}\vspace{-2.835pt} % Adjust this value
}

% Resume Item List %
\renewcommand{\labelitemii}{$\bullet$}
\newcommand{\ResumeItem}[2]{
  \item{
    \textbf{#1}{: #2 \vspace{-2.835pt}}
  }
}

\newcommand{\ResumeItemDefault}[1]{
  \item{
    #1 \vspace{-2.835pt}
  }
}

\newcommand{\ResumeProjectItem}[3]{
  \item{
    \href{#2}{\textbf{#1}}{: #3 \vspace{-2.835pt}}
  }
}

\newcommand{\ResumeSubItem}[2]{\ResumeItem{#1}{#2}\vspace{-2.835pt}}
\newcommand{\ResumeEntryStart}{\begin{itemize}[leftmargin=0mm, label={}]}
\newcommand{\ResumeEntryEnd}{\end{itemize}\vspace{-2.835pt}} % Adjust this value
\newcommand{\ResumeItemListStart}{\begin{itemize}[leftmargin=5mm, label=$\bullet$, itemsep=1mm, parsep=1mm]} % Adjust itemsep and parsep values
\newcommand{\ResumeItemListEnd}{\end{itemize}}
\newcommand{\ProjectItemListStart}{\begin{itemize}[leftmargin=*, label=$\bullet$]}
\newcommand{\ProjectItemListEnd}{\end{itemize}\vspace{\entryspacing}}

\newcommand{\OpenSourceProjectItem}[3]{
  \item{
    \href{#1}{\textbf{#2} }\hfill{#3}\vspace{-2.835pt}
  }
}


% Document %

\begin{document}
  \headertype{\address}{\phone}{\email}{\linkedin}{\github}{\website}
  
  \SectionHeading{Education}
  \ResumeEntryStart
    \ResumeEntryTSDL{Yale-NUS College} {Singapore}
    {Bachelor of Science (Honours) in Mathematics and Computer Science; GPA: 4.87/5.00} {May 2025}
    \ResumeSubItem{Relevant Coursework}{Asset Pricing, Statistical Inference, Stochastic Modelling, Machine Learning}
    \ResumeSubItem{Activities}{Teaching Assistant for Data Structures \& Algorithms, Probability Theory, and Databases}
    \ResumeSubItem{Awards}{Kewalram Chanrai Full Scholarship}
  \ResumeEntryEnd

  \vspace{5pt}

  \SectionHeading{Experience}

  \ResumeEntryStart
  \ResumeEntryTSDL{Caladan}{HFT Market Maker}{Algorithm Developer}{Jul 2025 – Present}
  \ResumeItemListStart
  \ResumeItemDefault{Automated daily post-trade analysis and transaction cost analysis for various trading algorithms, providing insights on hedge timing, execution quality, markout analysis, pricing, and other relevant statistics.}
  % \ResumeItemDefault{Collaborate with quantitative researchers and traders to uncover, backtest, and deploy new signals to improve overall execution quality, reducing slippage, improving fill rates, and minimizing overall execution costs.}
  \ResumeItemDefault{Built custom reporting pipelines to analyze and monitor algorithmic trading PnL, surfacing the risk of our strategy being arbitraged and assessing potential hedge ineffectiveness, alongside other key performance metrics.}
  \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
  \ResumeEntryTSDL{Caladan}{HFT Market Maker}{Algorithm Developer Intern}{May 2024 - Aug 2024}
  \ResumeItemListStart
  \ResumeItemDefault{Engineered low-latency trading execution servers and market quote polling services for new exchanges.}
  \ResumeItemDefault{Monitored and resolved production issues in core trading algorithms, ensuring correct trading behavior.}
  \ResumeItemDefault{Expanded Python analysis libraries for deeper insights into market volume, PnL, and trading statistics.}
  \ResumeItemDefault{Built ETL visibility tools and debugged out of memory issues in Python, reducing AWS costs by 80\%.}
  \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
    \ResumeEntryTSDL{Switcheo Labs}{Cryptocurrency Exchange}{Software Engineering Intern}{Oct 2022 - Dec 2022}
    \ResumeItemListStart
    \ResumeItemDefault{Automated market and liquidity pool allocation logic in Golang for DeFi trading across 90+ markets.}
    \ResumeItemDefault{Developed a TypeScript service for monitoring debt transactions and visualizing trades using React.}
    \ResumeItemDefault{Developed a Telegram bot to monitor and alert support of stalled Carbon blockchain trades.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  % \SectionHeading{Open Source}
  % \ResumeEntryStart
  % \OpenSourceProjectItem{https://github.com/panglesd/diffcessible}{panglesd/diffcessible}{Accessible Diff Viewer}
  % \ResumeItemListStart
  % \ResumeItemDefault{Designed and implemented optimized data structures (e.g., Zipper, blocks) and algorithms for word-level diff views in \textbf{OCaml}, improving file comparison granularity and navigation.}
  % \ResumeItemDefault{Programmed side-by-side view and integrated pager functionality for navigation of large diff outputs.}
  % % \ResumeItemDefault{Wrote a linear-space implementation of Myers diff and levenshtein distance algorithm in \textbf{OCaml}.}
  % \ResumeItemListEnd
  % \ResumeEntryEnd

  \ResumeEntryStart
    \ResumeEntryTSDL{Singular Asset Management}{Asset Management}{Equity Trading Intern}{Jan 2022 - Apr 2022}
    \ResumeItemListStart
      \ResumeItemDefault{Traded Indonesian equities on IDX, supporting a long-only portfolio with PM; generated 11\% returns.}
      % \ResumeItemDefault{Performed in-depth company analysis, industry research, competitor analysis, ESG analysis, and on-the-ground research to identify key trends across diverse sectors in Indonesia.}
      % \ResumeItemDefault{Created investment pitch decks, leveraging fundamental analysis to recommend long-term trading opportunities from the Jakarta Stock Exchange; generated a 27\% return on recommended picks.}
      % \ResumeItemDefault{Liaised with sell-side analysts and industry experts during broker calls and investor conferences to refine market perspectives and uncover new trading opportunities.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
  \ResumeEntryTSDL{Kredens Capital Management}{Hedge Fund}{Equity Trading Intern}{May 2022 – Aug 2022}
    \ResumeItemListStart
      \ResumeItemDefault{Researched US equities and macro trends to pitch short-term trades; generated 17\% portfolio returns.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \SectionHeading{Projects}
  \ProjectItemListStart
  \ResumeProjectItem{yokurang/mytree}
  {https://github.com/yokurang/mytree}
  {A published \textbf{Rust} tool for displaying directory trees with custom filters. 2k+ downloads.}
  \ResumeProjectItem{Strategy Behaviour Analysis}
  {https://github.com/yokurang/trading-strategy-behavior-analysis}
  {Investigated trade direction predictability using classification models.
  Engineered features and systematically trained and applied different models to understand trading behavior.}

  \ResumeProjectItem{Market Impact Analysis}
  {https://github.com/yokurang/trading-strategy-behavior-analysis}
  {Designed custom metrics and applied permutation-based hypothesis testing to evaluate the market impact of a live trading strategy.}

  \ResumeProjectItem{Strategy Markout Analysis}
  {https://github.com/yokurang/trading-strategy-markout-analysis}
  {Performed post-trade analysis on crypto data by identifying key one-hour windows, computing markouts, and visualizing strategy behaviour, trade profiles, and drawdowns.}
  \ProjectItemListEnd

  \SectionHeading{Skills}
  \ResumeEntryStart
    \ResumeItem{Languages}{ Python, Rust, C++, OCaml, C\#, TypeScript, JavaScript, SQL, Kotlin, Scala, Golang, Coq }
    \ResumeItem{Frameworks}{ React, Vue.js, Next.js, Express.js, Flask, Laravel, AWS (Lambda, DynamoDB) }
  \ResumeEntryEnd
\end{document}