\documentclass[letterpaper, 11pt]{article}

% ATS
\input{glyphtounicode}
\pdfgentounicode=1

% Packages
\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage[parfill]{parskip}

% Fonts 
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{hyperref}
% Computer Modern Font %
\usepackage{lmodern}

% Margins 
\usepackage[top=0.4in, bottom=0.4in, left=0.4in, right=0.4in]{geometry}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\def\sectionlineskip{\medskip} 
\def\sectionskip{\medskip} 
\def\namesize{\LARGE}

% URLs (Discouraged)
\hypersetup{
    colorlinks=true,
    linkcolor=black,   
    urlcolor=black,
}

% Customizations
\usepackage{tabularx}
\usepackage{array}
\usepackage{titlesec}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\pagestyle{empty}
\urlstyle{same}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Resume Header
\newcommand{\ResumeHeader}[6]{
  \noindent
  \begin{tabularx}{\textwidth}{>{\centering\arraybackslash}X}
    \namesize\MakeUppercase{\textbf{\fullname}} \\
    #1 \textbar\ #2 \\
    #3 \textbar\ #4 \textbar\ #5 \textbar\ #6 \\
  \end{tabularx}
}

% Header Settings %
\def \fullname { Alan Matthew }

\def \linkedinlink { https://www.linkedin.com/in/alan-matthew-yk }
\def \linkedintext { linkedin.com/in/alan-matthew-yk }

\def \phonenumber { +65 8047 3599 }

\def \githublink { https://github.com/yokurang }
\def \githubtext { github.com/yokurang }

\def \emaillink { mailto:alan.matthew.yk@gmail.com }
\def \emailtext { alan.matthew.yk@gmail.com }

\def \websitelink { https://yokurang.github.io/ }
\def \websitetext { yokurang.github.io/ }

\def \address { 9 Jalan Membina, Singapore }

\def \headertype {\ResumeHeader}

\def \entryspacing {-0pt}

\def \linkedin {\href{\linkedinlink}{\linkedintext}}
\def \phone {{\phonenumber}}
\def \email {\href{\emaillink}{\emailtext}}
\def \github {\href{\githublink}{\githubtext}}
\def \website {\href{\websitelink}{\websitetext}}

\newcommand{\SectionHeading}[1]{
  \sectionskip
  \raggedright\raggedbottom\MakeUppercase{\large{#1}}
  \sectionlineskip
  \hrule
  \color{black}
}

% Entry with Title, Subheading, Date, Location % 
\newcommand{\ResumeEntryTSDL}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r} 
      \textbf{#1} & #2 \\
      #3 & #4 \\
    \end{tabular*}\vspace{-2.835pt} % Adjust this value
}

% Resume Item List %
\renewcommand{\labelitemii}{$\bullet$}
\newcommand{\ResumeItem}[2]{
  \item{
    \textbf{#1}{: #2 \vspace{-2.835pt}}
  }
}

\newcommand{\ResumeItemDefault}[1]{
  \item{
    #1 \vspace{-2.835pt}
  }
}

\newcommand{\ResumeProjectItem}[3]{
  \item{
    \href{#2}{\textbf{#1}}{: #3 \vspace{-2.835pt}}
  }
}

\newcommand{\ResumeSubItem}[2]{\ResumeItem{#1}{#2}\vspace{-2.835pt}}
\newcommand{\ResumeEntryStart}{\begin{itemize}[leftmargin=0mm, label={}]}
\newcommand{\ResumeEntryEnd}{\end{itemize}\vspace{-2.835pt}} % Adjust this value
\newcommand{\ResumeItemListStart}{\begin{itemize}[leftmargin=5mm, label=$\bullet$, itemsep=1mm, parsep=1mm]} % Adjust itemsep and parsep values
\newcommand{\ResumeItemListEnd}{\end{itemize}}
\newcommand{\ProjectItemListStart}{\begin{itemize}[leftmargin=*, label=$\bullet$]}
\newcommand{\ProjectItemListEnd}{\end{itemize}\vspace{\entryspacing}}

\newcommand{\OpenSourceProjectItem}[3]{
  \item{
    \href{#1}{\textbf{#2} }\hfill{#3}\vspace{-2.835pt}
  }
}

\newcommand{\EduEntry}[4]{%
  \vspace{2pt}\noindent
  \begin{tabular*}{\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textnormal{#2} \\
    \multicolumn{2}{@{}l}{#3} \\
  \end{tabular*}\vspace{2pt}
}

\newcommand{\EduMeta}[3]{%
  {\normalsize
    \textbf{Coursework}: #1 \\
    \textbf{Activities}: #2 \\
    \textbf{Awards}: #3
  }\vspace{2pt}
}

% Document %

\begin{document}
  \headertype{\address}{\phone}{\email}{\linkedin}{\github}{\website}
  
\SectionHeading{Education}

% Yale-NUS
\EduEntry
  {Yale\textendash NUS College}
  {Aug 2020 -- May 2025}
  {Bachelor of Science (Honours) in Math, Computational and Statistical Sciences \textbar\ GPA: 4.87/5.00}
  {}
\EduMeta
  {Asset Pricing, Statistical Inference, Stochastic Modelling, Machine Learning}
  {Teaching Assistant for Data Structures \& Algorithms, Probability Theory, Statistical Inference}
  {Kewalram Chanrai Full Scholarship}

% UWC Li Po Chun
\EduEntry
  {UWC Li Po Chun}
  {Aug 2018 -- May 2020}
  {International Baccalaureate Diploma (40/45)}
  {}
\EduMeta
  {HL: Math, Physics, Chemistry (7/7/7)}
  {Working with Domestic Helper Club (US\$5,000 \& 250 books for Wonosobo library); United World Schools (US\$16,500 for schools in Yern Jas); Dragon Dance}
  {UWC Scholarship}

  \SectionHeading{Experience}

  \ResumeEntryStart
  \ResumeEntryTSDL{DRW}{HFT Proprietary Trading}{Incoming Quantitative Trading Analyst}{Jan 2026}
  \ResumeItemListStart
  \ResumeItemDefault{I will be trading stock options on the Hong Kong Stock Exchange, and researching and implementing high-frequency and mid-frequency trading strategies.}
  \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
  \ResumeEntryTSDL{Caladan (AlphaLab Capital)}{HFT Market Making}{Software Engineer}{Jul 2025 – Oct 2025}
  \ResumeItemListStart
  \ResumeItemDefault{Designed and built a generalized caching layer in Python to manage storage and fast retrieval of large-scale time-series data across S3, SQL, etc., reducing query latency and improving pipeline throughput by 97\%.}
  \ResumeItemDefault{Reimplemented ETL job services with fault-tolerance and async design (Python event loops, DAG modeling), improving recovery, consistency across dependent tasks, overall maintainability, and clarity of error reporting.}
  \ResumeItemDefault{Built a fault-tolerant 24/7 ETL service for real-time PnL computation, enforcing invariants for correctness and exposing statistics for business analysis, with infrastructure libraries supporting QuestDB and Grafana logs.}
  \ResumeItemDefault{Developed and maintained ETL pipelines, automating post-trade and transaction cost analysis (TCA) across high-frequency trading algorithms, delivering insights on hedge timing, execution quality, and price markouts.}
  \ResumeItemDefault{Designed and implemented robust NAV-based PnL attribution frameworks, producing granular breakdowns of performance by hedge leg, execution venue, etc., for comprehensive session-level trading reviews.}
  \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
  \ResumeEntryTSDL{Caladan (AlphaLab Capital)}{HFT Market Making}{Software Engineering Intern}{May 2024 - Aug 2024}
  \ResumeItemListStart
  \ResumeItemDefault{Implemented cold and hot path components for C\# trade servers, expanding crypto trading to new exchanges.}
  \ResumeItemDefault{Developed data ETL pipeline visibility service in Python; Rewrote core services using async to improve speed.}
  \ResumeItemDefault{Resolved critical bugs in algorithm trading logic and fixed out of memory issues, saving monthly costs by 80\%.}
  \ResumeItemDefault{Expanded Python analysis libraries for deeper insights into market volume, PnL, and trading statistics.}
  \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
    \ResumeEntryTSDL{Evooq}{Fintech SaaS}{Software Engineering Intern}{Jan 2024 - Apr 2024}
    \ResumeItemListStart
    \ResumeItemDefault{Created a Python LLM chatbot that translated natural language queries into SQL for a MariaDB database.}
    \ResumeItemDefault{Created a Python tool to generate trading ideas for a given portfolio with specific goals using RAG.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
    \ResumeEntryTSDL{Hatcher+}{Fintech SaaS}{Software Engineering Intern}{May 2023 - Aug 2023}
    \ResumeItemListStart
      \ResumeItemDefault{Developed a Python LLM microservice to parse excel company capitalization documents into structured JSONs.}
      \ResumeItemDefault{Programmed a PHP scheduler leveraging an LLM to predict English sentences and translate foreign languages.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
    \ResumeEntryTSDL{Switcheo Labs}{Cryptocurrency Exchange}{Software Engineering Intern}{Oct 2022 - Dec 2022}
    \ResumeItemListStart
    \ResumeItemDefault{Leveraged Golang to automatically link markets and liquidity pools, eliminating manual work and securely allocating USD \$130+ million of capital across the exchange.}
    \ResumeItemDefault{Implemented a microservice in TypeScript to monitor and collect data on CDP transactions and visualize trading activities using React, serving 35,000 daily visitors.}
    \ResumeItemDefault{Created a Golang API to aggregate and consolidate data from multiple databases into a single, unified API call, simplifying the information search process for 96,000+ users.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
    \ResumeEntryTSDL{Investree}{P2P Fintech Lending}{Software Engineering Intern}{Feb 2022 - Aug 2022}
    \ResumeItemListStart
      \ResumeItemDefault{Implemented new features using Vue.js and Kotlin to improve the presentation of financial statements and key metrics, boosting user reviews by 17\%.}
      \ResumeItemDefault{Designed and developed a covenant page from scratch using Vue.js and Kotlin, simplifying the contractual agreement process for over 59,000 business loans.}
      \ResumeItemDefault{Developed and deployed RESTful APIs in Kotlin for data querying, processing, and validation from Postgres databases, serving the frontend needs of over 100,000 users.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
    \ResumeEntryTSDL{Singular Asset Management}{Asset Management}{Equity Trading Intern}{Sep 2021 - Jan 2022}
    \ResumeItemListStart
      \ResumeItemDefault{Traded Indonesian equities on IDX, supporting a long-only portfolio with PM; generated 11\% returns.}
      \ResumeItemDefault{Performed in-depth company analysis, industry research, competitor analysis, ESG analysis, and on-the-ground research to identify key trends across diverse sectors in Indonesia.}
      \ResumeItemDefault{Liaised with sell-side analysts and industry experts during broker calls and investor conferences to refine market perspectives and uncover new trading opportunities.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \ResumeEntryStart
  \ResumeEntryTSDL{Kredens Capital Management}{Hedge Fund}{Equity Trading Intern}{May 2021 – Aug 2021}
    \ResumeItemListStart
      \ResumeItemDefault{Researched US equities and macro trends to pitch short-term trades; generated 17\% portfolio returns.}
      \ResumeItemDefault{Conducted detailed financial valuations and analyses of public companies in tech, aerospace, pharmaceutical, ride-hailing, defense, and gaming for potential trading opportunities.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \SectionHeading{Leadership}
  \ResumeEntryStart
    \ResumeEntryTSDL{Perception Gap}{International Network}{Founder}{Jul 2022 - Jul 2023}
    \ResumeItemListStart
      \ResumeItemDefault{Started and manage an international equity research club that grew from 4 friends to a global network of 17 members at institutions like Cornell, LSE, UPenn, Wellesley, HKU, and HKUST.}
      \ResumeItemDefault{Taught accounting and financial modelling to members, leading them to write comprehensive equity research reports on Tesla, Boeing, Lockheed Martin, Grab, and more.}
      \ResumeItemDefault{Organized mock interviews and quiz nights so members can network, sharpen business knowledge, and share market happenings—helping third-year members land investment banking and private equity internships.}
    \ResumeItemListEnd
  \ResumeEntryEnd

  \SectionHeading{Open Source}
  \ResumeEntryStart
  \OpenSourceProjectItem{https://github.com/panglesd/diffcessible}{panglesd/diffcessible}{Accessible Diff Viewer (OCaml)}
  \ResumeItemListStart
    \ResumeItemDefault{Developed side-by-side diff rendering with numbered lines, color highlighting, etc., to enhance user experience.}
    \ResumeItemDefault{Implemented data structures (e.g., zipper, block-based storage) and linear-space diff algorithms to enable precise word-level comparisons across multi-line changes and improve performance in large-scale file navigation.}
  \ResumeItemListEnd
  \ResumeEntryEnd

  \SectionHeading{Projects}
  \ProjectItemListStart
  \ResumeProjectItem{yokurang/poe2-arbitrage}
  {https://github.com/yokurang/path-of-elixe}
  {Engineered a scalable ETL and ML pipeline to scrape item prices/attributes and estimate FX rates via VWAP. Built both regularized regression and closed-form pricing models, selecting the best per item, and applied residual diagnostics in an iterative feedback loop to refine accuracy. Implemented a live client to continuously scan and detect undervalued items across multiple quote currencies in real time to users.}

  \ResumeProjectItem{yokurang/strategy-behaviour-analysis}
  {https://github.com/yokurang/trading-strategy-behavior-analysis}
  {Investigated trade direction predictability using classification models. Engineered features and systematically trained and applied different models to understand trading behavior.}

  \ResumeProjectItem{yokurang/mytree}
  {https://github.com/yokurang/mytree}
  {A published Rust tool for displaying directory trees with custom filters. 2k+ downloads.}

  \ResumeProjectItem{yokurang/strategy-markout-analysis}
  {https://github.com/yokurang/trading-strategy-markout-analysis}
  {Performed post-trade analysis on crypto data by identifying key one-hour windows, computing markouts, and visualizing strategy behaviour, trade profiles, and drawdowns.}

  \ResumeProjectItem{yokurang/passphrase-generator}
  {https://github.com/yokurang/passphrase-generator}
  {A \textbf{Rust} app to generate secure passphrases using Markov chains.}
  \ResumeProjectItem{yokurang/ocaml-chat}
  {https://github.com/yokurang/ocaml-chat}
  {An OCaml one-to-one chat app using TCP for real-time messaging and RTT.}
  \ProjectItemListEnd

  \SectionHeading{Skills}
  \ResumeEntryStart
    \ResumeItem{Languages}{ Python, Rust, C++, OCaml, C\#, TypeScript, JavaScript, SQL, Kotlin, Scala, Golang, Coq }
    \ResumeItem{Frameworks}{ React, Next.js, Flask, PyTorch, TensorFlow, scikit-learn, AWS (Lambda, DynamoDB) }
  \ResumeEntryEnd

\end{document}